{Gravitational wave sources in our Galactic backyard:}\\{Predictions for BHBH, BHNS and NSNS binaries detectable with LISA

### 2022-07-06 paper/tex/sections/appendix.tex
forgot to change one figure

Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate. By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses \citep[e.g.][]{Dominik+2015, Neijssel+2019, Kummer_thesis}. For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model. Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities. Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions do not include a high mass tail such as in our fiducial results.

>>>>

Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate. By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses \citep[e.g.][]{Dominik+2015, Neijssel+2019, Kummer_thesis}. For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution \edit1{for BHNSs} produced by the simulation using the simple Milky Way model. Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities. Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions do not include a high mass tail such as in our fiducial results.
